A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-22 paper.tex
Responding to some comments

\pavel{We need to introduce classical field theories linear over a commutative ring (used to talk about symmetries and the Hodge family).}

@@

@@

\begin{remark}
Again, in terms of the classical BV complex, this proposition tells us that given a classical BV complex of the form
\[\xymatrix{
\cdots \ar[r] & E_0^{-1}\ar[r] \ar[dr] \ar[ddr] &E_0^0 \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
&&E_1 \ar^{~}[dr] &E_1^! \ar[ur] && \\
&&E_1^! \ar^{~}[ur] &E_1 \ar[uur] && \\
}\]
with the differentials $E_1 \to E_1$ and $E_1^! \to E_1^!$ given by the identity, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify its differential and Lie structure. \chris{Pavel, is this, and the other remark above, what you wanted me to add?}
\end{remark}

@@

\begin{remark} \label{mapping_stack_remark}
The mapping stack above has a precise meaning in the language of derived algebraic geometry \chris{Let's say a few words about where the terminology comes from at least, even if for us it's just shorthand.  I can add this later.  I should also remark on the fact that we can pull the $T^*[d]$ out to a $T^*[k]$, with $k=-1$ if $X,Y,M$ are vector spaces.}  For the purposes of this paper, while we think of the derived stack as the global moduli space of solutions to the equations of motion in generalized BF theory, we will only use the perturbative datum of the classical BV complex.  The language of the mapping stack will simply be used as a compact way of referring to the theory above. 
\end{remark}

@@

\begin{eg}
There is a special case of this  of the ``holomorphic symplectic boson". 
\brian{include this?}
\end{eg}
\subsubsection{Generalized Hodge theory}
Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

@@

\begin{definition} \label{Hodge_family_def}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold. Fix an $L_\infty$ algebra $\fg$. We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$. The \defterm{generalized Hodge theory} is the $\CC[t]$-linear classical BV theory given by the generalized Chern--Simons theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$.
\end{definition}

>>>>

@@

We will also sometimes consider $\CC[t]$-families of classical field theories.  These will be defined as follows.
\begin{definition} \label{family_of_BV_theories_def}
A $\CC[t]$-family of classical BV theories is a quadruple $(E,Q_{\mr{BV}}, \omega, I)$ as before, but where now the classical BV differential is $t$-dependent.  In other words, it is given as a map
\[Q_{\mr{BV}} \colon \cE \to \cE  \otimes \CC[t] [1],\]
where, for each $t_0 \in \CC$, the quadruple $(E,Q^{t_0}_{\mr{BV}}, \omega, I)$
\[Q^{t_0}_{\mr{BV}} = \mr{ev}_{t_0} \circ Q_{\mr{BV}} \colon \cE \to \cE  \otimes \CC[t] [1] \to \cE[1]\]
defines a classical field theory.
\end{definition}

@@

\begin{remark}
Again, in terms of the classical BV complex, this proposition tells us that given a classical BV complex of the form
\[\xymatrix{
\cdots \ar[r] & E_0^{-1}\ar[r] \ar[dr] \ar[ddr] &E_0^0 \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
&&E_1 \ar^{~}[dr] &E_1^! \ar[ur] && \\
&&E_1^! \ar^{~}[ur] &E_1 \ar[uur] && \\
}\]
with the differentials $E_1 \to E_1$ and $E_1^! \to E_1^!$ given by the identity, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify its differential and Lie structure.
\end{remark}

@@

\begin{remark} \label{mapping_stack_remark}
The mapping stack above has a precise meaning in the language of derived algebraic geometry -- see for instance \cite{PTVV}, where, if $X, Y$ and $M$ are compact, such a mapping stack is shown to carry a $-1$-shifted symplectic structure.  For the purposes of this paper, while we think of the derived stack as the global moduli space of solutions to the equations of motion in generalized BF theory, we will only use the perturbative datum of the classical BV complex.  The language of the mapping stack will simply be used as a compact way of referring to the theory above. 
\end{remark}

@@

\begin{eg}
There is a special case of this, which one might label the ``holomorphic symplectic boson'' \cite[Definition 4.8]{SWchar}.  This is the case when $n_1 = 1$, $n_2 = n_3 = 0$, so $V$ is a $\fg$ representation with an ordinary symplectic structure.  If $V = T^*R$, we are considering the classical cotangent field theory whose classical solutions to the equations of motion model the cotangent bundle to $G$-bundles on a Riemann surface with a section of the associated bundle to $R$.
\end{eg}

\subsubsection{Generalized Hodge theory}
Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

@@

\begin{definition} \label{Hodge_family_def}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold. Fix an $L_\infty$ algebra $\fg$. We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$. The \defterm{generalized Hodge theory} is the $\CC[t]$-family of classical BV theories, as in Definition \ref{family_of_BV_theories_def}, given by the generalized Chern--Simons theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$.
\end{definition}
